---
title: "Analiza techniczna złota"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("../..")
source("./Src/Functions/ref.R")

g <- getSymbols("GOLD")

gold.first <- first(GOLD)
```

## Kurs złota

```{r}
 chartSeries(GOLD,theme=chartTheme('white'), type="line" ,TA=NULL)
```

# Bazując na średniej kroczącej

## MACD

```{r echo=F}
reChart()
addMACD()
```




## Bollinger Bands
```{r echo=F}
reChart()
addBBands()
#setTA()
```




## Welles Wilder's Directional Movement Indicator
```{r echo=F}
reChart()
addADX()
```

## Average True Range 
```{r echo=F}
addATR()
```


##  Aroon Indicator 
```{r echo=F}
addAroon()
```

## Aroon Oscillator 
```{r echo=F}
addAroonOsc()
```

## Commodity Channel Index 
```{r echo=F}
addCCI()
```

# Chaiken

## Chaiken Money Flow 
```{r echo=F}
addCMF()
```

## Chaiken Accumulation Distribution Line 
```{r echo=F}
addChAD()
```

## Chaiken Volatility 
```{r echo=F}
addChVol()
```

## Chande Momentum Oscillator 
```{r echo=F}
addCMO()
```


## Double Exponential Moving Average
```{r echo=F}
addDEMA()
```



##  Detrended Price Oscillator 
```{r echo=F}
addDPO()
```

## Exponential Moving Average
```{r echo=F}
addEMA()
```

## Arm's Ease of Movement
```{r echo=F}
addEMV()
```

## Moving Average Envelope 
```{r echo=F}
addEnvelope()
```

## Exponential Volume Weighted Moving Average  
```{r echo=F}
addEVWMA()
```

## options or futures expiration lines
```{r echo=F}
addExpiry()
```




## Know Sure Thing 
```{r echo=F}
addKST()
```

## Lines
```{r echo=F}
addLines()
```

## Moving Average Convergence Divergence
```{r echo=F}
chartSeries(GOLD,theme=chartTheme('white'), type="line" ,TA=NULL)
addMACD()
```

## Money Flow Index 
```{r echo=F}
addMFI()
```


## Momentum 
```{r echo=F}
addMomentum()
```

## On-Balance Volume 
```{r echo=F}
addOBV()
```


## Points
```{r echo=F}
#addPoints()
```

## Rate of Change
```{r echo=F}
addROC()
```

## Relative Strength Indicator 
```{r echo=F}
addRSI()
```
## Parabolic SAR 
```{r echo=F}
addSAR()
```
## Simple Moving Average
```{r echo=F}
addSMA()
```
## Stochastic Momentum Index
```{r echo=F}
addSMI()
```
## Trend Direction Index 
```{r echo=F}
addTDI()
```

##  Triple Smoothed Exponential Oscillator 
```{r echo=F}
addTRIX()
```

## Volume
```{r echo=F}
addVo()
```

## volatility
```{r echo=F}
addVolatility()
```

## Weighted Moving Average 
```{r echo=F}
addWMA()
```


## Williams Percent R 
```{r echo=F}
addWPR()
```

##  Zig Zag
```{r echo=F}
addZigZag()
```
## ZLEMA
```{r echo=F}
addZLEMA()
```
